Abb Analysis

### 2017-03-06 abbDataAnalysis_Script.Rmd
change model specifications

@@

  mod.ext.host <- glm(str.ext.pref~type+as.factor(bedbath)+
                        sub.mrkt+as.factor(host.type)+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
                        sub.mrkt+as.factor(host.type)+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)

>>>>

  str.data.ic$bedbath <- factor(str.data.ic$bedbath,
                                levels=c('1..1', '2..1', '2..2',
                                         '3..1', '3..2', '4..2'))

@@

  mod.ext.host <- glm(str.ext.pref~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
